---
title: "traineR Package"
author: "PROMiDAT"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{traineR}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  fig.align = "center",
  fig.width = 7,
  fig.height = 5
)
library(traineR)
```

The `traineR` package seeks to unify the different ways of creating predictive models and their different predictive formats. It includes methods such as K-Nearest Neighbors, Decision Trees, ADA Boosting, Extreme Gradient Boosting, Random Forest, Neural Networks, Deep Learning, Support Vector Machines, Bayesian and Logical Regression.

The main idea of the package is that all predictions can be execute using a standard syntax, also that all predictive methods can be used in the same way by default, for example, that all packages are use classification in their default invocation and all methods use a formula to determine the predictor variables (independent variables) and the response variable.

## Examples:

For the following examples we will use the `Puromycin` dataset:

```{r, echo=FALSE}
knitr::kable(head(Puromycin, 10))
```

```{r}
n <- seq_len(nrow(Puromycin))
.sample <- sample(n, length(n) * 0.7)
data.train <- Puromycin[.sample,]
data.test  <- Puromycin[-.sample,]
```

### Logistic Regression

**Modeling:**
```{r}
model <- train.glm(state~., data.train)
model
```

**Prediction as probability:**

**Note**: the result is always a matrix.

```{r}
prediction <- predict(model, data.test , type = "prob")
prediction
```

**Prediction as classification:**

**Note**: the result is always a factor.

```{r}
prediction <- predict(model, data.test , type = "class")
prediction
```

**Confusion Matrix**
```{r}
mc <- confusion.matrix(data.test, prediction)
mc
```

**Some Rates:**
```{r}
general.indexes(mc = mc)
```

### ADA Boosting

**Modeling:**
```{r}
model <- train.ada(state~., data.train, iter = 200)
model
```

**Prediction as probability:**
```{r}
prediction <- predict(model, data.test , type = "prob")
prediction
```

**Prediction as classification:**
```{r}
prediction <- predict(model, data.test , type = "class")
prediction
```

**Confusion Matrix:**
```{r}
mc <- confusion.matrix(data.test, prediction)
mc
```

**Some Rates:**
```{r}
general.indexes(mc = mc)
```

For the following examples we will use the `iris` dataset:

```{r, echo = FALSE}
knitr::kable(head(iris, 10))
```

```{r}
data("iris")
n <- seq_len(nrow(iris))
.sample <- sample(n, length(n) * 0.75)
data.train <- iris[.sample,]
data.test <- iris[-.sample,]
```

### Decision Trees

**Modeling:**
```{r}
model <- train.rpart(Species~., data.train)
model
```

**Prediction as probability:**
```{r}
prediction <- predict(model, data.test , type = "prob")
prediction
```

**Prediction as classification:**
```{r}
prediction <- predict(model, data.test , type = "class")
prediction
```

**Confusion Matrix:**
```{r}
mc <- confusion.matrix(data.test, prediction)
mc
```

**Some Rates:**
```{r}
general.indexes(mc = mc)
```

The model still supports the functions of the original package.

```{r message=FALSE, warning=FALSE}
library(rpart.plot)
prp(model, extra = 104, branch.type = 2, 
    box.col = c("pink", "palegreen3", "cyan")[model$frame$yval])
```


### Bayesian Method

**Modeling:**
```{r}
model <- train.bayes(Species~., data.train)
model
```

**Prediction as probability:**
```{r}
prediction <- predict(model, data.test , type = "prob")
prediction
```

**Prediction as classification:**
```{r}
prediction <- predict(model, data.test , type = "class")
prediction
```

**Confusion Matrix:**
```{r}
mc <- confusion.matrix(data.test, prediction)
mc
```

**Some Rates:**
```{r}
general.indexes(mc = mc)
```

### Random Forest

**Modeling:**
```{r}
model <- train.randomForest(Species~., data.train)
model
```

**Prediction as probability:**
```{r}
prediction <- predict(model, data.test , type = "prob")
prediction
```

**Prediction as classification:**
```{r}
prediction <- predict(model, data.test , type = "class")
prediction
```

**Confusion Matrix:**
```{r}
mc <- confusion.matrix(data.test, prediction)
mc
```

**Some Rates:**
```{r}
general.indexes(mc = mc)
```

The model still supports the functions of the original package.

```{r , message=FALSE, warning=FALSE}
library(randomForest)
varImpPlot(model)
```

### K-Nearest Neighbors

**Modeling:**
```{r}
model <- train.knn(Species~., data.train)
model
```

**Prediction as probability:**
```{r}
prediction <- predict(model, data.test , type = "prob")
prediction
```

**Prediction as classification:**
```{r}
prediction <- predict(model, data.test , type = "class")
prediction
```

**Confusion Matrix:**
```{r}
mc <- confusion.matrix(data.test, prediction)
mc
```

**Some Rates:**
```{r}
general.indexes(mc = mc)
```

### Neural Networks (nnet)

**Modeling:**
```{r}
model <- train.nnet(Species~., data.train, size = 20)
model
```

**Prediction as probability:**
```{r}
prediction <- predict(model, data.test , type = "prob")
prediction
```

**Prediction as classification:**
```{r}
prediction <- predict(model, data.test , type = "class")
prediction
```

**Confusion Matrix:**
```{r}
mc <- confusion.matrix(data.test, prediction)
mc
```

**Some Rates:**
```{r}
general.indexes(mc = mc)
```

### Neural Networks (neuralnet)

**Modeling:**
```{r}
model <- train.neuralnet(Species~., data.train, hidden = c(5, 7, 6),
                         linear.output = FALSE, threshold = 0.01, stepmax = 1e+06)
summary(model)
```

**Prediction as probability:**
```{r}
prediction <- predict(model, data.test , type = "prob")
prediction
```

**Prediction as classification:**
```{r}
prediction <- predict(model, data.test , type = "class")
prediction
```

**Confusion Matrix:**
```{r}
mc <- confusion.matrix(data.test, prediction)
mc
```

**Some Rates:**
```{r}
general.indexes(mc = mc)
```

### Support Vector Machines

**Modeling:**
```{r}
model <- train.svm(Species~., data.train)
model
```

**Prediction as probability:**
```{r}
prediction <- predict(model, data.test , type = "prob")
prediction
```

**Prediction as classification:**
```{r}
prediction <- predict(model, data.test , type = "class")
prediction
```

**Confusion Matrix:**
```{r}
mc <- confusion.matrix(data.test, prediction)
mc
```

**Some Rates:**
```{r}
general.indexes(mc = mc)
```

### Extreme Gradient Boosting

**Modeling:**
```{r}
model <- train.xgboost(Species~., data.train, nrounds = 79, maximize = FALSE, verbose = 0)
model
```

**Prediction as probability:**
```{r}
prediction <- predict(model, data.test , type = "prob")
prediction
```

**Prediction as classification:**
```{r}
prediction <- predict(model, data.test , type = "class")
prediction
```

**Confusion Matrix:**
```{r}
mc <- confusion.matrix(data.test, prediction)
mc
```

**Some Rates:**
```{r}
general.indexes(mc = mc)
```

